---
title: "Sentiment Analysis - Ebola"
author: "Ajinkya Sheth"
date: "June 13, 2019"
output: html_document
---


```{r setup, include=FALSE}
library(zoo)
library(dplyr)
library(pander)
library(tidytext)
library(tm)
library(ggplot2)
library(ggthemes)
library(tidyr)
#library(corpus)
library(wordcloud)
library(hash)
library(sf)
library(tmap)

library(raster)
library(spData)

library(sentimentr)
library(ggmap)

library(gganimate)

library(gifski)
library(transformr)

library(mapproj)

library(scales)
library(gridExtra)
SIERRALEONE_SHP <- read_sf('./SLE_adm3.shp')
```
```{r}
trigger <- read.csv(file="./Trigger_Other.csv", header=TRUE, sep=",", stringsAsFactors = FALSE)

```

```{r}
concerns=trigger$t_q6
questions=trigger$t_q7
risks=trigger$t_q8
byelaws=trigger$t_q9
discussions=trigger$t_q10
capability=trigger$t_q11

```


```{r}
concerns_df <- tibble(line = 1:length(concerns),text=concerns )
tidy_corpus <- concerns_df %>% 
  unnest_tokens(word, text)
data('stop_words')
tidy_corpus <- tidy_corpus %>% 
  anti_join(stop_words)


```

## 1 Explorations
### 1.1 Word Counts

```{r}
tidy_corpus %>%
  count(word, sort = TRUE) %>%
  filter(n > 100) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
    geom_col() +
    xlab(NULL) +
    coord_flip() +
  theme_tufte()
```

```{r}
tidy_corpus=tidy_corpus[tidy_corpus$word != "ebola",]
tidy_corpus=tidy_corpus[!is.na(tidy_corpus$word),]

corpus_sentiment <- tidy_corpus %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

word_counts <- tidy_corpus %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

```

### 1.2 Positive and Negative - Word Frequencies

```{r}
positive_sentiment <- corpus_sentiment %>%
  filter(sentiment>0) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip() +
  theme_tufte()
```

### 1.3 Positive and Negative - Word Clouds

```{r}
layout(matrix(c(1, 2), nrow=2), heights=c(1, 6))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, "Positive Sentiment")

word_counts %>%
  filter(sentiment=='positive') %>%
  with(wordcloud(word, n, max.words = 50))

layout(matrix(c(1, 2), nrow=2), heights=c(1, 6))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, "Negative Sentiment")
word_counts %>%
  filter(sentiment=='negative') %>%
  with(wordcloud(word, n, max.words = 50))
```

### 1.4 Sentimentr tests

sentimentr tests
```{r}
sentences_list <- c("I like ice-cream", 
                    "I do not like ice-cream", 
                    "I hate ice-cream", 
                    "I hardly like ice-cream",
                    "Do you think I like ice-cream?")

sentences_list %>%
  get_sentences() %>%
  sentiment


```

Notes for Sentiment by time:
- Two fields: mean sentiment as a function of a day
- Approx. Positive slope
- Two extremely negative peaks, indicate sentiment about concerns over entire country fell
- Terrible news can be a confounding factor

## 2 Sentiment by time

### 2.1 Mean Sentiment as a function of day

```{r}
A <-  (trigger %>%
  dplyr::select(Trig_date,District,Chiefdom,t_q6))

B <-  (trigger$t_q6 %>%
         get_sentences() %>%
  sentiment_by(by=NULL))

sentiment_concerns <- cbind(A,B)

sentiment_concerns$Trig_date <- as.Date(sentiment_concerns$Trig_date, "%m/%d/%Y")

concerns_by_day <- sentiment_concerns %>%
  dplyr::select(Trig_date,ave_sentiment)

concerns_by_day <- concerns_by_day %>%
  group_by(Trig_date) %>%
  summarise(mean_sent = mean(ave_sentiment, na.rm = TRUE), std_sent = sd(ave_sentiment, na.rm = TRUE))

require(ggplot2)
ggplot( data = concerns_by_day, aes( x=Trig_date, y=value, color=variable)) + 
  geom_line(aes(y=mean_sent, color = "mean_sent")) + 
  geom_line(aes(y=std_sent, color = "std_sent")) + 
  ggtitle('Mean Sentiment') + 
  scale_x_date(labels = date_format("%m-%d-%y"), breaks = "3 week")

#geom_point()

concerns_by_day
```

### 2.2 Mean Sentiment as a function of month

```{r}
A <-  (trigger %>%
  dplyr::select(Trig_date,District,Chiefdom,t_q6))

B <-  (trigger$t_q6 %>%
         get_sentences() %>%
  sentiment_by(by=NULL))

sentiment_concerns_cuts <- cbind(A,B)

sentiment_concerns_cuts$Trig_date <- as.Date(sentiment_concerns_cuts$Trig_date, "%m/%d/%Y")
sentiment_concerns_cuts$Trig_month <- as.Date(cut(sentiment_concerns_cuts$Trig_date,breaks = "month"))
sentiment_concerns_cuts$Trig_week <- as.Date(cut(sentiment_concerns_cuts$Trig_date,breaks = "week",start.on.monday = FALSE))

concerns_by_week <- sentiment_concerns_cuts %>%
  dplyr::select(Trig_week,ave_sentiment)

concerns_by_week <- concerns_by_week %>%
  group_by(Trig_week) %>%
  summarise(mean_sent = mean(ave_sentiment, na.rm = TRUE), std_sent = sd(ave_sentiment, na.rm = TRUE))

concerns_by_month <- sentiment_concerns_cuts %>%
  dplyr::select(Trig_month, ave_sentiment)

concerns_by_month <- concerns_by_month %>%
  group_by(Trig_month) %>%
  summarise(mean_sent = mean(ave_sentiment, na.rm = TRUE), 
            std_sent = sd(ave_sentiment, na.rm = TRUE),
            cv_sent = cv(ave_sentiment,na.rm = TRUE))

ggplot( data = concerns_by_month, aes( x=Trig_month, y=value, color=variable)) + 
  geom_line(aes(y=mean_sent, color = "mean_sent"), size=2) + 
  geom_line(aes(y=std_sent, color = "std_sent"),size =2) +
  ggtitle('Mean Sentiment over months') +
  scale_x_date(labels = date_format("%y-%m"), breaks = "1 month")

```

### 2.3 Mean Sentiment as a function of week

```{r}
ggplot( data = concerns_by_week, aes( x=Trig_week, y=value, color=variable)) + 
  geom_line(aes(y=mean_sent, color = "mean_sent"),size=2) + 
  geom_line(aes(y=std_sent, color = "std_sent"),size=2) + 
  ggtitle('Mean Sentiment over weeks') +
  scale_x_date(labels = date_format("%y-W%W"), breaks = "3 week")
```


## 3 Sentiment by space


```{r}
concerns_by_chiefdom <- sentiment_concerns %>%
  dplyr::select(District, Chiefdom, ave_sentiment)

concerns_by_chiefdom <- concerns_by_chiefdom %>%
  group_by(District,Chiefdom) %>%
  summarise(mean_ave = mean(ave_sentiment, na.rm = TRUE))


concerns_by_district <- sentiment_concerns %>%
  dplyr::select(District, ave_sentiment)

concerns_by_district <- concerns_by_district %>%
  group_by(District) %>%
  summarise(mean_sent = mean(ave_sentiment, na.rm = TRUE),
            sd_sent = sd(ave_sentiment,na.rm = TRUE),
            cv_sent = cv(ave_sentiment,na.rm = TRUE))

counts_by_district <- sentiment_concerns %>%
  dplyr::select(District) %>%
  group_by(District) %>%
  summarise(count_sent = n())

head(concerns_by_district)

```

### 3.1 Number of trigger visits across districts

```{r}
shp <- read_sf('./shp1/SLE_adm2.shp')
district_df<-data.frame(shp$NAME_2,shp$geometry)

plt <- ggplot()


counts_plot <- district_df %>%
  left_join(counts_by_district,by=c("shp.NAME_2"="District"))
#write.csv(data.frame(shp$admin3Name,shp$admin3RefN,shp$admin2Name),file = "ShapeFile3.csv")

plt + geom_sf(data = counts_plot, aes(fill=count_sent)) + scale_fill_gradient2(low='red',high='green',mid = 'yellow', midpoint = 800) + ggtitle("Number of trigger visits across Districts")

```


### 3.2 Mean sentiment across districts
Notes and interpretations about sentiment by space:
- Freetown and another district missing from the data
- south-western part more negative sentiment
- Measures against ebola may be better in other parts of the country 

```{r}
concerns_plot<-district_df %>%
  left_join(concerns_by_district,by=c("shp.NAME_2"="District"))
#write.csv(data.frame(shp$admin3Name,shp$admin3RefN,shp$admin2Name),file = "ShapeFile3.csv")
plt <- ggplot()
plt + geom_sf(data = concerns_plot, aes(fill=mean_sent)) + scale_fill_gradient2(low='red',high='green', mid='yellow',midpoint=-0.075) + ggtitle("Mean of Sentiments across Districts")
```

### 3.3 SD of sentiments across districts

```{r}
sd_max <- max(concerns_plot[!is.na(concerns_plot$sd_sent),]$sd_sent)
sd_min <- min(concerns_plot[!is.na(concerns_plot$sd_sent),]$sd_sent)
sd_mid <- (sd_max+sd_min)/2
plt <- ggplot()
plt + geom_sf(data = concerns_plot, aes(fill=sd_sent)) + scale_fill_gradient2(low='red',high='green', mid='yellow', midpoint=sd_mid) + ggtitle("Standard Deviation of Sentiments across Districts")
```
### 3.4 Co-efficient of variation of sentiments across districts

```{r}
cv_max <- max(concerns_plot[!is.na(concerns_plot$cv_sent),]$cv_sent)
cv_min <- min(concerns_plot[!is.na(concerns_plot$cv_sent),]$cv_sent)
cv_mid <- (cv_max+cv_min)/2
plt <- ggplot()
plt + geom_sf(data = concerns_plot, aes(fill=cv_sent)) + scale_fill_gradient2(low='red',high='green', mid='yellow', midpoint=cv_mid) + ggtitle("Variation of Sentiments across Districts")
```

```{r}
head(concerns_plot)
```

## 4 Sentiment by time and space

### 4.1 Mean sentiment by months across districts

```{r}

concerns_dis_mon <- sentiment_concerns %>%
  dplyr::select(Trig_date,District, ave_sentiment)

concerns_dis_mon$Trig_date <- as.Date(as.yearmon(concerns_dis_mon$Trig_date))
#concerns_dis_mon$Trig_date <- as.Date(concerns_dis_mon$Trig_date, "%b %Y")

concerns_dis_mon <- concerns_dis_mon %>%
  group_by(District,Trig_date) %>%
  summarise(mean_sent = mean(ave_sentiment, na.rm = TRUE))

concerns_dis_mon
ggplot( data = concerns_dis_mon, aes(x=Trig_date, y=mean_sent)) + geom_line(aes(color = District), size=2) + ggtitle('Mean Sentiment') + scale_x_date(name="Trig_date", date_labels = "%b %Y", breaks="month" )
```
### 4.2 Mean sentiment by weeks across districts

```{r}
concerns_dis_week <- sentiment_concerns %>%
  dplyr::select(Trig_date,District, ave_sentiment)

concerns_dis_week$Trig_week <- as.Date(cut(concerns_dis_week$Trig_date,breaks = "week",start.on.monday = FALSE))

concerns_dis_week <- concerns_dis_week %>%
  group_by(District,Trig_week) %>%
  summarise(mean_sent = mean(ave_sentiment, na.rm = TRUE))

concerns_dis_week
ggplot( data = concerns_dis_week, aes(x=Trig_week, y=mean_sent)) + geom_line(aes(color = District)) + ggtitle('Mean Sentiment over weeks') + scale_x_date(name="Trig_week", date_labels = "%y-W%W", breaks="3 week" )
```


### 4.3 Mean sentiment by months across district (Animation)

```{r}

concerns_month_geo <-district_df %>%
  left_join(concerns_dis_mon,by=c("shp.NAME_2"="District"))

concerns_month_geo <- concerns_month_geo[!is.na(concerns_month_geo$Trig_date),]


concerns_month_geo_animate <- ggplot() + geom_sf(data = concerns_month_geo, aes(fill=mean_sent,frame=Trig_date)) + scale_fill_gradient2(low='red',high='green', mid='white',midpoint=0) + transition_states(Trig_date, wrap=TRUE) + coord_sf() + theme_tufte() + labs(title = "Date") 
## animate plot with gganimate
animate(concerns_month_geo_animate, fps=3)

#anim_save("animation.gif",animation=last_animation())

#concerns_month_geo$Trig_month

#concerns_month_geo

```



